\documentclass[12pt]{article}
\usepackage[pdfborder={0 0 0.5 [3 2]}]{hyperref}%
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}%
\usepackage[shortalphabetic]{amsrefs}%
\usepackage{amsmath}
\usepackage{enumerate}
% \usepackage{enumitem}
\usepackage{amssymb}                
\usepackage{amsmath}                
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{bbm}
\usepackage[table,xcdraw]{xcolor}
\usepackage{tikz}
\usepackage{float}
\usepackage{booktabs}
\usepackage{svg}
\usepackage{mathtools}
\usepackage{cool}
\usepackage{url}
\usepackage{graphicx,epsfig}
\usepackage{makecell}
\usepackage{array}

\def\noi{\noindent}
\def\T{{\mathbb T}}
\def\R{{\mathbb R}}
\def\N{{\mathbb N}}
\def\C{{\mathbb C}}
\def\Z{{\mathbb Z}}
\def\P{{\mathbb P}}
\def\E{{\mathbb E}}
\def\Q{\mathbb{Q}}
\def\ind{{\mathbb I}}

\DeclareMathOperator{\spn}{span}
\DeclareMathOperator{\ran}{ran}

\graphicspath{ {periodic/} }

\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{hypothesis}{Hypothesis}

\newtheorem{notation}{Notation}

\begin{document}

\subsection*{Conjugation Lemma}

I am curious if we can use the Conjugation Lemma to simplify things. Here is a version of the Conjugation Lemma, which is adapted and cleaned up from Zum2018.

\begin{lemma}[Conjugation Lemma]
Let $W \in \C^N$, and consider the family of ODEs on $\R$

\begin{equation}\label{LambdaEVPconj}
W(x)' = A(x; \Lambda) W(x) + F(x) 
\end{equation}

where $\Lambda \in \Omega \subset C^m$ is a parameter vector. Take the same assumptions as in the Gap Lemma, i.e. 

\begin{enumerate}
	\item The map $\Lambda \mapsto A(\cdot; \Lambda)$ is analytic in $\Lambda$.
	\item $A(x; \Lambda) \rightarrow A_\pm(\lambda)$ (independent of $\Lambda$) as $x \rightarrow \pm \infty$, and for $|\Lambda| < \delta$ we have the uniform exponential decay estimates 
	\begin{align}
	\left| \frac{\partial^k}{\partial x^k} A(x; \Lambda) - A_\pm(\Lambda) \right| 
	&\leq C e^{-\theta |x|} && 0 \leq k \leq K
	\end{align}
	where $\alpha > 0$, $C > 0$, and $K$ is a nonnegative integer.
\end{enumerate}

Then in a neighborhood of any $\Lambda_0 \in \Omega$ there exist invertible linear transformations

\begin{align*}
P_+(x, \Lambda) &= I + \Theta_+(x, \Lambda) \\
P_-(x, \Lambda) &= I + \Theta_-(x, \Lambda) 
\end{align*}

defined on $\R^+$ and $\R^-$, respectively, such that

\begin{enumerate}[(i)]
\item The change of coordinates $W = P_\pm Z$ reduces \eqref{LambdaEVPconj} to the equations on $\R^\pm$

\begin{align}
Z' = A^\pm(\Lambda) Z + G(x; \Lambda)
\end{align}

where

\[
G(x; \Lambda) = P_\pm (x, \Lambda)^{-1} F(x)
\]

\item For any fixed $0 < \tilde{\theta} < \theta$, $0 \leq k \leq K+1$, and $j \geq 0$ we have the decay rates
\begin{align*}
\left| \partial_\Lambda^j \partial_x^k \Theta_\pm \right| \leq C(j, k)e^{-\tilde{\theta}|x|}
\end{align*}
\end{enumerate}
\begin{proof}
I have written out the proof somewhere else for the case where $F(x) = 0$, which essentially follows Zum2018 but fills in more details. Only a small modification is necessary for $F(x) \neq 0$.
\end{proof}
\end{lemma}

\subsection*{The Problem}

We want to do Lin's method on the eigenvalue problem for KdV5 with periodic BCs. (Eventually, we may try this for the case on the real line). Recall that from the existence problem, we write the $n-$pulse piecewise as

\[
(q_n)_i^\pm(x) = q^\pm(x; \beta_i^\pm) + u_i^\pm(x)
\]

Note that by the existence problem, this is smooth, especially at $x = 0$.\\

The piecewise eigenvalue problem is

\begin{align*}
&(W_i^\pm)' = A( (q_n)_i^\pm; \lambda ) W_i^\pm + \lambda^2 d_i \tilde{H}_i^\pm \\
&W_i^-(0) = W_i^+(0) \\
&W_i^\pm(0) \in \C \Psi(0) \oplus Y^+ \oplus Y^- \oplus Y^0 \\
&W_i^+(X_i) - W_{i+1}^-(-X_i) = D_i d
\end{align*}

where

\begin{align*}
A((q_n)_i^\pm(x); \lambda) &=  \begin{pmatrix}0 & 1 & 0 & 0 & 0 \\0 & 0 & 1 & 0 & 0 \\0 & 0 & 0 & 1 & 0 \\0 & 0 & 0 & 0 & 1 \\
2 \partial_x (q_n)_i^\pm(x) + \lambda & 2 (q_n)_i^\pm(x) - c & 0 & 1 & 0 \end{pmatrix} \\
D_i d &= d_{i+1}[(Q_n)_{i+1}'(-X_i) + \lambda \partial_c (Q_n)_{i+1}(-X_i)]
- d_i [ (Q_n)_i'(X_i) + \lambda \partial_c (Q_n)_i(-X_i) ] \\
\end{align*}

and we have nice estimates/bounds

\begin{align*}
|H(x)|, |\tilde{H}_i^\pm(x)| &\leq C e^{-\alpha |x|} \\
|\Delta H_i^\pm| &= |\tilde{H}_i^\pm - H| \leq C(e^{-\alpha X_i} + e^{-\alpha X_{i-1}} ) \\
D_i d &= ( Q'(X_i) + Q'(-X_i))(d_{i+1} - d_i ) + \mathcal{O} \left( e^{-\alpha X_i} \left( |\lambda| +  e^{-\alpha X_i}  \right) |d| \right) \\
\end{align*}

The way we approach this (as in San98) is to look at the (piecewise) variational equation

\[
(W_i^\pm)' = A(q^\pm(x; \beta_i^\pm); \lambda) W_i^\pm
\]

and use the variation of constants formula together with an exponential dichotomy (or trichotomy).\\

What we really want is to use the Conjugation Lemma so that the evolution of the variational equation does not depend on $\lambda$ (or on the $\beta_i^\pm$, but those are less important and should be taken care of automatically since the exponential decay to the asymptotic operator does not depend on them). We take $\Lambda = (\lambda)$ in the conjugation lemma. $A((q_n)_i^\pm; \lambda)$ is linear, thus analytic, in $\lambda$, so we should be all set.\\

Using the Conjugation Lemma, make the substitution $W_i^\pm = P_i^\pm Z_i^\pm$, where $P_i^\pm$ conjugates $A((q_n)_i^\pm; \lambda)$. Then the problem should look like

\begin{align*}
&(Z_i^\pm(x))' = A(0; \lambda) Z_i^\pm(x) + \lambda^2 d_i P_i^\pm(x; \lambda)^{-1} \tilde{H}_i^\pm(x) \\
&P_i^-(0; \lambda) Z_i^-(0) = P_i^+(0; \lambda) Z_i^+(0) \\
&P_i^\pm(0; \lambda) Z_i^\pm(0) \in \C \Psi(0) \oplus Y^+ \oplus Y^- \oplus Y^0 \\
&P_i^+(X_i; \lambda) Z_i^+(X_i)\ - P_{i+1}^-(-X_i; \lambda) Z_{i+1}^-(-X_i; \lambda) = D_i d
\end{align*}

Note that the asymptotic matrix $A(0; \lambda)$ is the same for $\R^\pm$, so that is good.\\

Advantage: The first equation is way simpler, i.e. reduced to the constant coefficient case. I think this is worth it, and I hope it reduces the nightmarish estimates.\\

Disadvantage: We have $P_i^\pm$ in all the matching conditions. For the matching conditions at $\pm X_i$, these are approximately the identity, so this should not be a big deal. For the matching conditions at 0, they could cause trouble.\\

Since $A(0; \lambda)$ is constant coefficient (and we know what it is), we don't have to bother with the exponential trichotomy stuff, since everything evolves in the eigenspaces of $A(0; \lambda)$, which do not depend on $x$. Before we proceed, make the following hypothesis.

\begin{hypothesis}\label{Aspectrumhyp}
\begin{enumerate}
	\item The spectrum of $A(0; 0)$ has isolated, simple eigenvalues at $\{ 0, \pm \alpha_0 \pm \beta_0 \}$, where $\alpha_0, \beta_0 > 0$. The real part of any other eigenvalue of $A(0; 0)$ lies outside the interval $[-\alpha_0, \alpha_0]$.
\end{enumerate}
\end{hypothesis}

We then define the following.

\begin{enumerate}
	\item Let

	\begin{align*}
	X_m &= \min(X_0, \dots, X_{n-1}) \\
	X_M &= \max(X_0, \dots, X_{n-1}) \\
	\end{align*}

	\item Let $n_-$ be the number of eigenvalues of $A(0; 0)$ with negative real part, and $n_+$ be the number of eigenvalues of $A(0; 0)$ with positive real part. Then, by Hypothesis \ref{Aspectrumhyp}, $n_-, n_+ \geq 2$, and $n_- + n_+ + 1 = m$.

	\item Let $\nu(\lambda)$ be the simple, small eigenvalue of $A(0; \lambda)$. By Hypothesis \ref{Aspectrumhyp}, $\nu(0) = 0$, and $\nu(\lambda) = \mathcal{O}(\lambda)$. 

	\item Let $\rho > 0$, $\delta > 0$ be a small. How small will be determined later. We will take $|\lambda| < \delta$.

	\item Let $\alpha = \alpha_0 - \rho$. We choose $\delta$ sufficiently small so that for all $|\lambda| < \delta$,

	\begin{enumerate}
		\item $|\nu(\lambda)| < \rho$
		\item The real part of any other eigenvalue of $A(0; \lambda)$ lies outside the interval $[-\alpha, \alpha]$.
	\end{enumerate}

	\item Let $\tilde{\alpha} = \alpha - 2 \rho > 0$.

	\item Choose $X_m$ sufficiently large so that
	\begin{equation}
	e^{-\alpha X_m}, |\lambda|, ||\Delta H|| < \delta
	\end{equation}

\end{enumerate}

Let $P^{u/s/c}_0(\lambda)$ be the eigenprojections for the unstable/stable/center subspaces $E^{u/s/c}(\lambda)$ of $A(0; \lambda)$. The center subspace is a legit center subspace only when $\nu(\lambda)$ has no real part, e.g. when $\lambda = 0$, but we will always call it a center subspace for convenience. Let $\Phi(x, y; \lambda) = e^{A(0; \lambda)(x-y)}$ be the evolution of the constant-coefficient ODE

\[
Z' = A(0; \lambda) Z
\]

Let $\Phi^{u/s/c}(x, y; \lambda)$ be the evolutions on the respective eigenspaces. Since $E_c(\lambda)$ is one-dimensional, we have in particular that

\begin{align*}
\Phi^c(x, y; \lambda) v &= e^{\nu(\lambda)(x - y)} v && v \in E^c(\lambda)
\end{align*}

We have the bounds

\begin{align*}
|\Phi^s(x, y; \lambda)| &\leq C e^{-\alpha(x - y)} \\
|\Phi^u(x, y; \lambda)| &\leq C e^{-\alpha(y - x)} \\
|\Phi^c(x, y; \lambda)| &\leq C e^{-\rho|x - y|} 
\end{align*}

We are going to want to relate things to the variational/adjoint variational problem for the nontransformed system. We have a distinct (but only to leading order) variational equations for each of the $n$ pieces.

\begin{align*}
V_i' &= A((q_n)_i; \lambda) V_i \\
W_i' &= -A((q_n)_i; \lambda)^* W_i
\end{align*}

$(Q_n)_i'(x)$ solves the variational problem, and we have solutions $\Psi_i(x)$ and $1$ to the adjoint variational problem. This is conjugated by $P_i^\pm(x; 0)$. Let $\Theta_i(y, x; \lambda)$ be the evolution for the untransformed variational equations. We would like to relate this to the evolution of the transformed equation. We should have for appropriate values of $x, y$

\[
\Theta_i(y, x; \lambda) = P_i^\pm(y; \lambda) \Phi(y, x; \lambda) P_i^\pm(x; \lambda)^{-1}
\]

We can also go the other way if we like.\\

At this point, we will modify the projections in Lin's method slightly. This should not make any difference. Instead of using the coordinate system based on $Q'(0)$, we will use the $n$ coordinate systems based off of $(Q_n)_i'(0)$. Defining the spaces $Y_i^{+/-/0}$ in the same way, we now have the system of equations

\begin{align*}
&(Z_i^\pm(x))' = A(0; \lambda) Z_i^\pm(x) + \lambda^2 d_i P_i^\pm(x; \lambda)^{-1} \tilde{H}_i^\pm(x) \\
&P_i^-(0; \lambda) Z_i^-(0) = P_i^+(0; \lambda) Z_i^+(0) \\
&P_i^\pm(0; \lambda) Z_i^\pm(0) \in \C \Psi_i(0) \oplus Y_i^+ \oplus Y_i^- \oplus Y_i^0 \\
&P_i^+(X_i; \lambda) Z_i^+(X_i)\ - P_{i+1}^-(-X_i; \lambda) Z_{i+1}^-(-X_i; \lambda) = D_i d
\end{align*}

What we hope happens is that we get a result involiving $(Q_n)_i'$ and $\Psi_i$, and then we use the fact that these are close to $Q'$ and $\Psi$.\\

Define the spaces

\begin{align*}
V_a &= \bigoplus_{i=0}^{n-1} E^u(\lambda) \oplus E^s(\lambda) \\
V_b &= \bigoplus_{i=0}^{n-1} E^u(0) \oplus E^s(0) \\
V_c^+ &= \bigoplus_{i=0}^{n-1} E^c(\lambda) \\
V_c^- &= \bigoplus_{i=0}^{n-1} E^c(\lambda) \\
V_c &= V_c^+ \oplus V_c^- \\
V_\lambda &= B_\delta(0) \subset \C
\end{align*}

where the subscripts are all $\mod n$, as in the existence problem. We use the $\lambda-$dependent eigenspaces for $a_i^\pm$ and $c_i^\pm$, since we will be evolving them under the $\lambda-$dependent evolution. All the product spaces are endowed with the maximum norm, e.g. for $V_c$, $|c| = \max(|c_0^-|, \dots, |c_{n-1}^-|, |c_0^+|, \dots, |c_{n-1}^+|)$. In addition, we take the following convention: if we eliminate either a subscript or a superscript (or both) in the norm, we are taking the maximum over the eliminated thing. For example,
\begin{enumerate}
	\item $|c_i| = \max(|c_i^+|, |c_i^-|)$ 
	\item $|c^+| = \max(|c_0^+|, \dots, |c_{n-1}^+|)$
\end{enumerate}

\subsection*{The Inversion}

At this point, we can write down the fixed point equations for the problem. For $i = 0, \dots, n-1$, the fixed point equations are

\begin{align*}
Z_i^-(x) &= \Phi^s(x, -X_{i-1}; \lambda) a_{i-1}^- + \Phi^u(x, 0; \lambda) b_i^- + \Phi^c(x, -X_{i-1}; \lambda) c_{i-1}^- \\
&+ \lambda^2 d_i \int_0^x \Phi^u(x, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy
+ \lambda^2 d_i \int_{-X_{i-1}}^x \Phi^s(x, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy \\
&+ \lambda^2 d_i \int_{-X_{i-1}}^x \Phi^c(x, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy  \\ 
Z_i^+(x) &= \Phi^u(x, X_i; \lambda) a_i^+ + \Phi^s(x, 0; \lambda) b_i^+ + \Phi^c(x, X_i; \lambda) c_i^+ \\
&+ \lambda^2 d_i \int_0^x \Phi^s(x, y; \lambda) P_i^+(y; \lambda)^{-1} \tilde{H}_i^+(y) dy
+ \lambda^2 d_i \int_{X_i}^x \Phi^u(x, y; \lambda) P_i^+(y; \lambda)^{-1} \tilde{H}_i^+(y) dy \\
&+ \lambda^2 d_i \int_{X_i}^x \Phi^c(x, y; \lambda) P_i^+(y; \lambda)^{-1} \tilde{H}_i^+(y) dy \\
\end{align*}

Note that $Z_i^\pm$ only appears on the LHS, so we don't need to do the first inversion step as in San98. We can start with the matching conditions at $\pm X_i$.

\subsubsection*{Matching at ends}

Here, we solve the condition

\[
P_i^+(X_i; \lambda) Z_i^+(X_i) - P_{i+1}^-(-X_i; \lambda) Z_{i+1}^-(-X_i; \lambda) = D_i d
\]

At $\pm X_i$, the fixed point equations become

\begin{align*}
Z_{i+1}^-(-X_i) &= a_i^- + \Phi^u(-X_i, 0; \lambda) b_{i+1}^- + c_i^- 
+ \lambda^2 d_i \int_0^{-X_i} \Phi^u(-X_i, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy \\ 
Z_i^+(X_i) &= a_i^+ + \Phi^s(X_i, 0; \lambda) b_i^+ + c_i^+ 
+ \lambda^2 d_i \int_0^{X_i} \Phi^s(X_i, y; \lambda) P_i^+(y; \lambda)^{-1} \tilde{H}_i^+(y) dy
\end{align*}

We use here the fact that, for example, $a_i^- \in E^s(\lambda)$ and $\Phi^s(-X_{i-1}, -X_{i-1}; \lambda)$ is the identity on $E^s(\lambda)$. Thus we need to solve

\begin{align*}
D_i d &= P_i^+(X_i; \lambda) Z_i^+(X_i) - P_{i+1}^-(-X_i; \lambda) Z_{i+1}^-(-X_i; \lambda) \\
&= P_i^+(X_i; \lambda) a_i^+ + P_i^+(X_i; \lambda) \Phi^s(X_i, 0; \lambda) b_i^+ + P_i^+(X_i; \lambda) c_i^+ \\
&+ \lambda^2 d_i P_i^+(X_i; \lambda) \int_0^{X_i} \Phi^s(X_i, y; \lambda) P_i^+(y; \lambda)^{-1} \tilde{H}_i^+(y) dy \\
&- P_{i+1}^-(X_i; \lambda) a_i^- - P_{i+1}^-(X_i; \lambda) \Phi^u(-X_i, 0; \lambda) b_{i+1}^- - P_{i+1}^-(X_i; \lambda) c_i^- \\
&- \lambda^2 d_i P_{i+1}^-(X_i; \lambda) \int_0^{-X_i} \Phi^u(-X_i, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy 
\end{align*}

From the Conjugation Lemma, we have

\begin{equation}\label{conjest}
P_i^\pm(\pm X_i; \lambda) = I + \mathcal{O}(e^{-\alpha X_i})
\end{equation}

which we will use on the $a_i^\pm$ and $c_i^\pm$ terms. For bounds on the other terms we have

\[
|P_i^+(X_i; \lambda) \Phi^s(X_i, 0; \lambda)b_i^+| \leq C e^{-\alpha X_i} |b_i^+|
\]

and

\begin{align*}
\left|
P_i^+(X_i; \lambda) \int_0^{X_i} \Phi^s(X_i, y; \lambda) P_i^+(y; \lambda)^{-1} \tilde{H}_i^+(y) dy \right| 
&\leq C \int_0^{X_i} e^{-\alpha(X_i - y)}e^{-\alpha y} dy \\
&\leq C \int_0^{X_i} e^{-(\alpha - \rho)(X_i - y)}e^{-\alpha y} dy \\
&= C e^{-(\alpha - \rho) X_i} \int_0^{X_i} e^{-\rho y} dy \\ 
&\leq C e^{-(\alpha - \rho) X_i} 
\end{align*}

The ``negative'' pieces are similar. Thus we have

\begin{align}\label{Dideq1}
D_i d &= a_i^+ - a_i^- + c_i^+ - c_i^- + L_1(\lambda)_i(a, b, c^+, c^-, d)
\end{align}

where

\[
|L_1(\lambda)_i(a, b, c^+, c^-, d)| \leq C \Big( e^{-\alpha X_i} |a_i| + e^{-\alpha X_i} (|b_i^+| + |b_{i+1}^-|) + e^{-\alpha X_i} (|c_i^+| + |c_i^-|) + e^{-(\alpha - \rho) X_i} |\lambda^2| |d| \Big)
\]

Following San98 (and leaving out some steps), we can solve this for $(a, c^+)$ to get $(a_i, c_i^+) = A_1(\lambda)_i(b, c_i^-, d)$, with bound

\begin{align*}
|A_1&(\lambda)_i(b, c^-, d)|
\leq C \Big( e^{-\alpha X_i} (|b_i^+| + |b_{i+1}^-|) + |c_i^-| + (e^{-(\alpha - \rho) X_i} |\lambda^2| + |D_i|)|d| \Big)
\end{align*} 

As in San98, we hit \eqref{Dideq1} with projections on the various eigenspaces $E^{s/u/c}(\lambda)$. The remainder term $A_2(\lambda)_i^c(b, d)$ is found by substituting the bound for $A_1$ into $L_1$ and simplifying.

\begin{align*}
a_i^+ &= P_0^u(\lambda) D_i d + A_2(\lambda)_i^+(b, c^-, d) \\
a_i^- &= -P_0^s(\lambda) D_i d + A_2(\lambda)_i^-(b, c^-, d) \\
c_i^+ &= c_i^- + P_0^c(\lambda) D_i d + A_2(\lambda)_i^c(b, c^-, d) )
\end{align*}

where we have bound

\begin{align*}
|A_2&(\lambda)_i(b, d)|
\leq C \Big( e^{-\alpha X_i} (|b_i^+| + |b_{i+1}^-|) + e^{-\alpha X_i} |c_i^-| + e^{-(\alpha - \rho) X_i} |\lambda|^2|d| + e^{-\alpha X_i} |D_i||d| \Big)
\end{align*} 

For the first two, this is not quite what we want. Anticipating what we will need later, we write this as

\begin{align*}
a_i^+ = P_i^+(X_i; \lambda)a_i^+ + (I - P_i^+(X_i; \lambda))a_i^+ &= P_0^u(\lambda) D_i d + A_2(\lambda)_i^+(b, c^-, d)
\end{align*}

Rearranging this, we obtain

\begin{align*}
P_i^+(X_i; \lambda)a_i^+ &= P_0^u(\lambda) D_i d + A_2(\lambda)_i^+(b, c^-, d) - (I - P_i^+(X_i; \lambda))a_i^+ \\
&= P_0^u(\lambda) D_i d + A_2(\lambda)_i^+(b, c^-, d) + \mathcal{O}\Big( e^{-\alpha X_i} (|b_i^+| + |b_{i+1}^-| + |c_i^-| + (|\lambda^2| + |D_i|)|d|)\Big)
\end{align*}

where we used the bound $A_1$ and the estimate \eqref{conjest}. The last term on the RHS is the same (or higher) order as $A_2$, so we incorporate that into $A_2(\lambda)_i^+(b, c^-, d)$ to get

\begin{align*}
P_i^+(X_i; \lambda)a_i^+ &= P_0^u(\lambda) D_i d + A_2(\lambda)_i^+(b, c^-, d)
\end{align*}

Finally, we operate on both sides on the left by $P_i^+(X_i; \lambda)^{-1}$ to solve for $a_i^+$. This is a bounded operator, so we will also incorporate this into $A_2(\lambda)_i^+(b, c^-, d)$ (with the same bound). Thus we have

\begin{align*}
a_i^+ &= P_i^+(X_i; \lambda)^{-1} P_0^u(\lambda) D_i d + A_2(\lambda)_i^+(b, c^-, d)
\end{align*}

The same thing works for $a_i^-$, giving us

\begin{align*}
a_i^+ &= P_i^+(X_i; \lambda)^{-1} P_0^u(\lambda) D_i d + A_2(\lambda)_i^+(b, c^-, d) \\
a_i^- &= -P_i^-(-X_i; \lambda)^{-1} P_0^s(\lambda) D_i d + A_2(\lambda)_i^-(b, c^-, d)
\end{align*}

For the third one, we would like to evaluate and get an estimate for $P_0^c(\lambda) D_i d$. To do that, recall that the actual expression for $D_i d$ is 

\begin{align*}
D_i d &= d_{i+1}[(Q_n)_{i+1}'(-X_i) + \lambda \partial_c (Q_n)_{i+1}(-X_i)]
- d_i [ (Q_n)_i'(X_i) + \lambda \partial_c (Q_n)_i(-X_i) ] \\
&= d_{i+1} (Q_n)_{i+1}'(-X_i) - d_i (Q_n)_i'(X_i) + \mathcal{O}(|\lambda|e^{-\alpha X_i}|d|)
\end{align*}

For the leading order piece, we have

\begin{align*}
d_{i+1} &(Q_n)_{i+1}'(-X_i) - d_i (Q_n)_i'(X_i) \\
&= d_{i+1} P_{i+1}^-(-X_i; 0)(Q_n)_{i+1}'(-X_i) - d_i P_i^+(X_i; 0)(Q_n)_i'(X_i) + \mathcal{O}(e^{-2 \alpha X_i}|d|) \\
&= d_{i+1} P_{i+1}^-(-X_i; \lambda)(Q_n)_{i+1}'(-X_i) - d_i P_i^+(X_i; \lambda)(Q_n)_i'(X_i) + \mathcal{O}(e^{-\alpha X_i}(|\lambda| + e^{-\alpha X_i})|d|)\\
\end{align*}

The leading order terms here are in $E^{s/u}(\lambda)$, and so are eliminated by $P_0^c(\lambda)$, which leaves us with

\[
P_0^c(\lambda) D_i d = \mathcal{O}(e^{-\alpha X_i}(|\lambda| + e^{-\alpha X_i})|d|)
\]

\subsubsection*{Matching at 0}

The next is to satisfy the conditions

\begin{align*}
P_i^\pm(0; \lambda) Z_i^\pm(0) &\in \C \Psi_i(0) \oplus Y_i^0 \oplus Y_i^+ \oplus Y_i^- \\
P_i^+(0; \lambda) Z_i^+(0) - P_i^-(0; \lambda) Z_i^-(0) &\in \C \Psi_i(0) \oplus Y_i^0
\end{align*}

Note that these conditions do depend on $i$. Recall that for each $i$ we have

\[
\C^m = \C \Psi_i(0) \oplus \C (Q_n)_i'(0) \oplus Y_i^0 \oplus Y_i^+ \oplus Y_i^- 
\]

This condition is equivalent to the three projections

\begin{align*}
P(\C (Q_n)_i'(0) ) P_i^-(0; \lambda) Z_i^-(0) &= 0 \\
P(\C (Q_n)_i'(0) ) P_i^+(0; \lambda) Z_i^+(0) &= 0 \\
P(Y_i^+ \oplus Y_i^-) ( P_i^+(0; \lambda) Z_i^+(0) - P_i^-(0; \lambda) Z_i^-(0) ) &= 0
\end{align*}

where the kernel of each projection is the remaining spaces in the direct sum. We don't need $\C (Q_n)_i'(0)$ in the third equation since we eliminated any component in it in the first two equations.\\

Recall that for $\lambda = 0$, the tangent space to the stable manifold at $x = 0$ is spanned by $Y_i^+$ and $(Q_n)_i'(0)$, and the tangent space to the unstable manifold at $x = 0$ is spanned by $Y_i^-$ and $(Q_n)_i'(0)$. Thus we have

\begin{align*}
P_i^-(0; 0)^{-1} (Q_n)_i'(0) &= v^- \in E^u(0) \\
P_i^+(0; 0)^{-1} (Q_n)_i'(0) &= v^+ \in E^s(0)
\end{align*}

Let

\begin{align*}
E^u(0) &= \C v^- \oplus E^- \\
E^s(0) &= \C v^+ \oplus E^+ \\
\end{align*}

Then we have

\begin{align*}
P_i^-(0; 0)^{-1} Y^- = E^- \\
P_i^+(0; 0)^{-1} Y^+ = E^+ \\
\end{align*}

Next, following San98, we decompose $b_i^\pm$ uniquely as $b_i^\pm = x_i^\pm + y_i^\pm$, where $x_i^\pm \in \C v^\pm$ and $y_i^\pm \in E^\pm$.\\

At $x = 0$, the fixed point equations become

\begin{align*}
Z_i^-(0) &= \Phi^s(0, -X_{i-1}; \lambda) a_{i-1}^- + P_0^u(\lambda) b_i^- + \Phi^c(0, -X_{i-1}; \lambda) c_{i-1}^- \\
&+ \lambda^2 d_i \int_{-X_{i-1}}^0 \Phi^s(0, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy 
+ \lambda^2 d_i \int_{-X_{i-1}}^0 \Phi^c(0, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy  \\ 
Z_i^+(0) &= \Phi^u(0, X_i; \lambda) a_i^+ + P_0^s(\lambda) b_i^+ + \Phi^c(0, X_i; \lambda) c_i^+ \\
&+ \lambda^2 d_i \int_{X_i}^0 \Phi^u(0, y; \lambda) P_i^+(y; \lambda)^{-1} \tilde{H}_i^+(y) dy 
+ \lambda^2 d_i \int_{X_i}^0 \Phi^c(0, y; \lambda) P_i^+(y; \lambda)^{-1} \tilde{H}_i^+(y) dy \\
\end{align*}

Doing a little manipulation, and using the known form of the evolution $\Phi^c$, we have

\begin{align*}
Z_i^-(0) &= \Phi^s(0, -X_{i-1}; \lambda) a_{i-1}^- + x_i^- + y_i^- + (P_0^u(\lambda) - P_0^u(0))b_i^- + e^{\nu(\lambda) X_{i-1}} c_{i-1}^- \\
&+ \lambda^2 d_i \int_{-X_{i-1}}^0 \Phi^s(0, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy 
+ \lambda^2 d_i \int_{-X_{i-1}}^0 \Phi^c(0, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy  \\ 
Z_i^+(0) &= \Phi^u(0, X_i; \lambda) a_i^+ + x_i^+ + y_i^+ + (P_0^s(\lambda) - P_0^s(0)) b_i^+ + e^{-\nu(\lambda)X_i} c_i^+ \\
&+ \lambda^2 d_i \int_{X_i}^0 \Phi^u(0, y; \lambda) P_i^+(y; \lambda)^{-1} \tilde{H}_i^+(y) dy 
+ \lambda^2 d_i \int_{X_i}^0 \Phi^c(0, y; \lambda) P_i^+(y; \lambda)^{-1} \tilde{H}_i^+(y) dy \\
\end{align*}

Since $c_i^\pm$ are in the eigenspaces $E^c(\lambda)$, we do some further manipulation to separate out a component in $E^c(0)$.

\begin{align*}
Z_i^-(0) &= \Phi^s(0, -X_{i-1}; \lambda) a_{i-1}^- + x_i^- + y_i^- + (P_0^u(\lambda) - P_0^u(0))b_i^- \\
&+ e^{\nu(\lambda) X_{i-1}} P_0^c(0) c_{i-1}^- + e^{\nu(\lambda) X_{i-1}} (P_0^c(\lambda) - P_0^c(0))c_{i-1}^- \\
&+ \lambda^2 d_i \int_{-X_{i-1}}^0 \Phi^s(0, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy 
+ \lambda^2 d_i \int_{-X_{i-1}}^0 \Phi^c(0, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy  \\ 
Z_i^+(0) &= \Phi^u(0, X_i; \lambda) a_i^+ + x_i^+ + y_i^+ + (P_0^s(\lambda) - P_0^s(0)) b_i^+ \\
&+ e^{-\nu(\lambda)X_i} P_0^c(0) c_i^+ + e^{-\nu(\lambda)X_i} (P_0^c(\lambda) - P_0^c(0))c_i^+ \\
&+ \lambda^2 d_i \int_{X_i}^0 \Phi^u(0, y; \lambda) P_i^+(y; \lambda)^{-1} \tilde{H}_i^+(y) dy 
+ \lambda^2 d_i \int_{X_i}^0 \Phi^c(0, y; \lambda) P_i^+(y; \lambda)^{-1} \tilde{H}_i^+(y) dy \\
\end{align*}
 
Before we take projections, we operate on these with the conjugation operators $P_i^\pm(0; \lambda)$. Where needed, we will use $P_i^\pm(0; \lambda) = P_i^\pm(0; 0) + \mathcal{O}(|\lambda|)$ (from the Taylor expansion). If we do that, then take the projections, we eventually wind up with a equation of the form

\[
\begin{pmatrix}x_i^- \\ x_i^+ \\ 
y_i^+ - y_i^- \end{pmatrix} + L_2(\lambda)_i(b, \tilde{c}, d) = 0
\]

where we define

\begin{equation}\label{tildec}
\tilde{c}_i^\pm = e^{\pm \nu(\lambda) X_i} c_i^-
\end{equation}

To get a bound on $L_2$, we need to bound the individual terms above.

\begin{enumerate}

\item For the $a_i$ terms, we substitute the bound for $A_1(\lambda)$ to get

\begin{align*}
|P_i^-(0; \lambda) \Phi^s(0, -X_{i-1}; \lambda) a_{i-1}^-|
&\leq C \Big( e^{-2 \alpha X_{i-1}} (|b_{i-1}^+| + |b_i^-|) + e^{-\alpha X_{i-1}}|c_{i-1}^-| + e^{-\alpha X_{i-1}}(e^{-\tilde{\alpha} X_{i-1}} |\lambda^2| + |D_{i-1}|)|d| \Big) \\
|P_i^+(0; \lambda) \Phi^u(0, X_i; \lambda) a_i^+|
&\leq C \Big( e^{-2 \alpha X_i} (|b_i^+| + |b_{i+1}^-|) + e^{-\alpha X_i} |c_i^-| + e^{-\alpha X_i} (e^{-\tilde{\alpha} X_i} |\lambda^2| + |D_i|)|d| \Big)
\end{align*}

Substituting the $\tilde{c}$, these become

\begin{align*}
|P_i^-(0; \lambda) \Phi^s(0, -X_{i-1}; \lambda) a_{i-1}^-|
&\leq C \Big( e^{-2 \alpha X_{i-1}} (|b_{i-1}^+| + |b_i^-|) + e^{-\tilde{\alpha} X_{i-1}}|\tilde{c}_{i-1}^+| + e^{-\alpha X_{i-1}}(e^{-\tilde{\alpha} X_{i-1}} |\lambda^2| + |D_{i-1}|)|d| \Big) \\
|P_i^+(0; \lambda) \Phi^u(0, X_i; \lambda) a_i^+|
&\leq C \Big( e^{-2 \alpha X_i} (|b_i^+| + |b_{i+1}^-|) + e^{-\tilde{\alpha} X_i} |\tilde{c}_i^-| + e^{-\alpha X_i} (e^{-\tilde{\alpha} X_i} |\lambda^2| + |D_i|)|d| \Big)
\end{align*}

\item For the $b_i$ terms, we have

\[
|P_i^-(0; \lambda)(P_0^u(\lambda) - P_0^u(0))b_i^-| \leq C |\lambda||b_i^-| 
\]

We also have from the projection

\begin{align*}
P_i^-(0; \lambda)( x_i^- + y_i^- ) = P_i^-(0; 0)( x_i^- + y_i^- ) + \mathcal{O}(|\lambda||b_i^-|)
\end{align*}

\item For the $c_i^-$ terms, we have

\begin{align*}
P_i^-(0; \lambda)&[ e^{\nu(\lambda) X_{i-1}} P_0^c(0) c_{i-1}^- + e^{\nu(\lambda) X_{i-1}} (P_0^c(\lambda) - P_0^c(0))c_{i-1}^-] \\
&= P_i^-(0; 0) P_0^c(0) \tilde{c}_{i-1}^+ + (P_i^-(0; \lambda) - P_i^-(0; 0)) P_0^c(0) \tilde{c}_{i-1}^+ + P_i^-(0; \lambda) (P_0^c(\lambda) - P_0^c(0)) \tilde{c}_{i-1}^+ \\
&= P_i^-(0; 0) P_0^c(0) \tilde{c}_{i-1}^+ + \mathcal{O}(|\lambda||\tilde{c}_{i-1}^+|)
\end{align*}

Note that the leading order term here is eliminated by all the projections.

\item The $c_i^+$ terms are the same, except we have to use $A_2$ to write $c_i^+$ in terms of $c_i^+$. Using the bound for $A_2$ and the estimate for $P_0^c(\lambda) D_i d$, we obtain

\begin{align*}
e^{-\nu(\lambda)X_i} c_i^+ &= e^{-\nu(\lambda)X_i} c_i^- 
+ e^{-\nu(\lambda)X_i} P_0^c(\lambda) D_i d + e^{-\nu(\lambda)X_i} A_2(\lambda)_i^c(b, d)\\
&= e^{-\nu(\lambda)X_i} c_i^- + \mathcal{O}\Big( e^{\rho X_i} e^{-\alpha X_i} ( |\lambda| + e^{-\alpha X_i} ) |d|) + e^{-(\alpha - \rho) X_i}( |b_i^+| + |b_{i+1}^-| + |c_i^-| + e^{\rho X_i}|\lambda^2||d| + |D_i||d|) \Big) \\
&= e^{-\nu(\lambda)X_i} c_i^- + \mathcal{O}\Big( e^{-\tilde{\alpha} X_i} ( |\lambda||d| + e^{-\alpha X_i} |d| + |b_i^+| + |b_{i+1}^-| + |\tilde{c}_i^+| + |\lambda^2||d| + |D_i||d|) \Big) \\
&= e^{-\nu(\lambda)X_i} c_i^- + \mathcal{O}\Big( e^{-\tilde{\alpha} X_i} ( |b_i^+| + |b_{i+1}^-| + |\tilde{c}_i^+| + (|\lambda| + e^{-\alpha X_i} + |D_i| ) |d|) \Big) \\
&= e^{-\nu(\lambda)X_i} c_i^- + \mathcal{O}\Big( e^{-\tilde{\alpha} X_i} ( |b_i^+| + |b_{i+1}^-| + |\tilde{c}_i^+| + (|\lambda| + |D_i| ) |d|) \Big) \\
\end{align*}

Thus we have

\begin{align*}
P_i^+(0; \lambda)&[ e^{-\nu(\lambda) X_i} P_0^c(0) c_i^+ + e^{-\nu(\lambda) X_{i-1}} (P_0^c(\lambda) - P_0^c(0))c_i^+] \\
&= P_i^-(0; 0) P_0^c(0) \tilde{c}_i^- + \mathcal{O}(|\lambda||\tilde{c}_i^-|)
+ \mathcal{O}\Big( e^{-\tilde{\alpha} X_i} ( |b_i^+| + |b_{i+1}^-| + |\tilde{c}_i^+| + (|\lambda| + |D_i| ) |d|) \Big)
\end{align*}

Again, the leading order term is eliminated by all the projections.

\item The bound on the integral terms is determined by the bound on the center subspace, since there is potential growth in that subspace.

\begin{align*}
\left| \lambda^2 d P_i^-(0; \lambda) \int_{-X_{i-1}}^0 \Phi^c(0, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy \right| &\leq C |\lambda|^2 |d| \int_{-X_{i-1}}^0 e^{\rho y} e^{-\alpha y} dy \\
&\leq C |\lambda|^2 |d|
\end{align*}

\end{enumerate}

Putting all these together, we obtain the bound for $L_2(\lambda)_i(b, \tilde{c}, d)$.

\begin{align*}
L_2(\lambda)_i(b, \tilde{c}, d) &\leq 
C\Big( (|\lambda| + e^{-\tilde{\alpha}X_m})|b| 
+ (|\lambda| + e^{-\tilde{\alpha}X_{i-1}})|\tilde{c}_{i-1}^+|
+ (|\lambda| + e^{-\tilde{\alpha}X_i})|\tilde{c}_i^-| \\
&+ (e^{-\tilde{\alpha}X_{i-1}}|D_{i-1}| + e^{-\tilde{\alpha}X_i}|D_i| 
+ |\lambda|^2)|d| \Big)
\end{align*}

Peforming the inversion, we solve for $b$ to get $B_1(\lambda)(\tilde{c}, d)$, which has bound

\begin{align*}
|B_1(\lambda)_i(\tilde{c}, d)| \leq C \Big(
(|\lambda| + e^{-\tilde{\alpha}X_{i-1}})|\tilde{c}_{i-1}^+|
+ (|\lambda| + e^{-\tilde{\alpha}X_i})|\tilde{c}_i^-|
+ (e^{-\tilde{\alpha}X_{i-1}}|D_{i-1}| + e^{-\tilde{\alpha}X_i}|D_i| 
+ |\lambda|^2)|d|
\Big)
\end{align*}

A more uniform bound is

\begin{align*}
|B_1(\lambda)(\tilde{c}, d)| \leq C \Big(
(|\lambda| + e^{-\tilde{\alpha}X_{i-1}})|\tilde{c}_{i-1}^+|
+ (|\lambda| + e^{-\tilde{\alpha}X_i})|\tilde{c}_i^-|
+ (e^{-\tilde{\alpha}X_m}|D| 
+ |\lambda|^2)|d|
\Big)
\end{align*}

We keep the $\tilde{c}^\pm$ terms separate, since that might end up mattering. We can plug this into the bounds for $A_2$ to get $A_4$ with bound

\begin{align*}
|A_4&(\lambda)_i(\tilde{c}, d)|
\leq C \Big( 
e^{-\alpha X_i} (|\lambda| + e^{-\tilde{\alpha}X_{i-1}})|\tilde{c}_{i-1}^+|
+ e^{-\alpha X_i}(|\lambda| + e^{-\tilde{\alpha}X_i})(|\tilde{c}_i^+| + |\tilde{c}_i^-|)
+ e^{-\alpha X_i}(|\lambda| + e^{-\tilde{\alpha}X_{i+1}})|\tilde{c}_{i+1}^-| \\
&+ e^{-(\alpha - \rho) X_i} |\lambda|^2|d| + e^{-\alpha X_m}|D||d| \Big)
\end{align*} 

A uniform bound is

\begin{align*}
|A_4&(\lambda)_i(\tilde{c}, d)|
\leq C \Big( 
e^{-\alpha X_m} (|\lambda| + e^{-\tilde{\alpha}X_m})|\tilde{c}|
+ e^{-(\alpha - \rho) X_i} |\lambda|^2|d| + e^{-\alpha X_m}|D||d| \Big)
\end{align*} 

Now that we have solved (uniquely) for everything except for the $c_i^-$ and $d$, we are ready to compute the jump conditions in the two directions.

\subsubsection*{Jump in Psi direction}

For this jump, we project on $\Psi_i(0)$.

\[
\xi_i = \langle \Psi_i(0), P_i^+(0; \lambda) Z_i^+(0) - P_i^-(0; \lambda) Z_i^-(0) \rangle
\]

Recall that $Z_i^\pm(0)$ are given by

\begin{align*}
Z_i^-(0) &= \Phi^s(0, -X_{i-1}; \lambda) a_{i-1}^- + b_i^- + (P_0^u(\lambda) - P_0^u(0))b_i^- \\
&+ e^{\nu(\lambda) X_{i-1}} P_0^c(0) c_{i-1}^- + e^{\nu(\lambda) X_{i-1}} (P_0^c(\lambda) - P_0^c(0))c_{i-1}^- \\
&+ \lambda^2 d_i \int_{-X_{i-1}}^0 \Phi^s(0, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy 
+ \lambda^2 d_i \int_{-X_{i-1}}^0 \Phi^c(0, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy  \\ 
Z_i^+(0) &= \Phi^u(0, X_i; \lambda) a_i^+ + b_i^+ + (P_0^s(\lambda) - P_0^s(0)) b_i^+ \\
&+ e^{-\nu(\lambda)X_i} P_0^c(0) c_i^+ + e^{-\nu(\lambda)X_i} (P_0^c(\lambda) - P_0^c(0))c_i^+ \\
&+ \lambda^2 d_i \int_{X_i}^0 \Phi^u(0, y; \lambda) P_i^+(y; \lambda)^{-1} \tilde{H}_i^+(y) dy 
+ \lambda^2 d_i \int_{X_i}^0 \Phi^c(0, y; \lambda) P_i^+(y; \lambda)^{-1} \tilde{H}_i^+(y) dy \\
\end{align*}

We will compute the significant terms first. The noncenter integral will give us the Melnikov integral. For the ``minus'' piece, we have

\begin{align*}
&\langle \Psi_i(0), P_i^-(0; \lambda) \int_{-X_{i-1}}^0 \Phi^s(0, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy \rangle \\
&= \int_{-X_{i-1}}^0 \langle \Psi_i(0), P_i^-(0; \lambda), \Phi^s(0, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}(y) \rangle dy \\
&= \int_{-X_{i-1}}^0 \langle \Psi_i(0), P_i^-(0; \lambda), \Phi^s(0, y; \lambda) P_i^-(y; \lambda)^{-1} H(y) \rangle dy + \mathcal{O}({e^{-\alpha X_m}})\\
&= \int_{-X_{i-1}}^0 \langle \Psi_i(0), \Theta_i^s(0, y; \lambda) H(y) \rangle dy + \mathcal{O}({e^{-\alpha X_m}})\\
&= \int_{-X_{i-1}}^0 \langle \Psi_i(0), \Theta_i^s(0, y; 0) H(y) \rangle dy + \mathcal{O}(|\lambda| + {e^{-\alpha X_m}})\\
&= \int_{-X_{i-1}}^0 \langle \Theta_i^s(y, 0; 0)^* \Psi_i(0), H(y) \rangle dy + \mathcal{O}(|\lambda| + {e^{-\alpha X_m}})\\
&= \int_{-X_{i-1}}^0 \langle \Psi_i(y), H(y) \rangle dy + \mathcal{O}(|\lambda| + {e^{-\alpha X_m}})\\
&= \int_{-X_{i-1}}^0 \langle \Psi(y), H(y) \rangle dy + \mathcal{O}(|\lambda| + {e^{-\alpha X_m}})\\
\end{align*}

Note that in the last step, we put this in terms of $\Psi(x)$, the solution to the adjoint variational problem for the primary pulse.\\

Next, we look at the terms involving $a$. For these, we plug in $A_4$.

\begin{align*}
\langle &\Psi_i(0), P_i^-(0; \lambda) \Phi^s(0, -X_{i-1}; \lambda) a_{i-1}^- \rangle \\
&= \langle \Psi_i(0), P_i^-(0; \lambda) \Phi^s(0, -X_{i-1}; \lambda) (- P_i^-(-X_{i-1}; \lambda)^{-1} P_0^s(\lambda) D_{i-1} d + A_4(\lambda)_i^-(\tilde{c}, d)) \rangle \\
&= -\langle \Psi_i(0), \Theta_i^s(0, -X_{i-1}; \lambda) P_0^s(\lambda) D_{i-1} d \rangle + \mathcal{O}( e^{-(\alpha + \tilde{\alpha})X_m}(|\tilde{c}| + |\lambda|^2 |d| + |D||d|) \\
&= -\langle \Psi_i(0), \Theta_i^s(0, -X_{i-1}; 0) P_0^s(0) D_{i-1} d \rangle + \mathcal{O}( e^{-(\alpha + \tilde{\alpha})X_m}(|\tilde{c}| + |\lambda||d| + |D||d|) \\
&= -\langle \Theta_i^s(-X_{i-1}, 0; 0)^* \Psi_i(0), P_0^s(0) D_{i-1} d \rangle + \mathcal{O}( e^{-(\alpha + \tilde{\alpha})X_m}(|\tilde{c}| + |\lambda||d| + |D||d|) \\
&= -\langle \Psi_i(-X_{i-1}), P_0^s(0) D_{i-1} d \rangle + \mathcal{O}( e^{-(\alpha + \tilde{\alpha})X_m}(|\tilde{c}| + (|\lambda| + |D|)|d|) \\
\end{align*}

The remaining terms will be higher order. Doing these in turn, we have

\begin{enumerate}
\item For the terms involving $b$,

\begin{align*}
\langle \Psi(0), P_i^-(0; \lambda) \Phi^u(0, 0; \lambda) b_i^- \rangle
&= \langle \Psi(0), (P_i^-(0; 0) + \mathcal{O}(|\lambda|))(I + \mathcal{O}(|\lambda|)) b_i^- \rangle \\
&= \langle \Psi(0), P_i^-(0; 0) b_i^- \rangle + \mathcal{O}(|\lambda||b_i^-|) \\
&= |\lambda| \Big(
(|\lambda| + e^{-\tilde{\alpha}X_m})|\tilde{c}|
+ (e^{-\tilde{\alpha}X_m}|D| 
+ |\lambda|^2)|d|
\Big)
\end{align*}

where we substituted in $B_1$.

\item For the terms involving $\tilde{c}$, we have

\begin{align*}
\langle \Psi(0), P_i^-(0; \lambda)e^{\nu(\lambda) X_{i-1}} P^c(\lambda) c_{i-1}^-\rangle &= 
\langle \Psi(0), (P_i^-(0; 0) + \mathcal{O}(\lambda))(I + \mathcal{O}(\lambda)) \tilde{c}_{i-1}^+ \rangle \\
&= \mathcal{O}(|\lambda|) \tilde{c}_{i-1}^+
\end{align*}

We also have to do the same substitution as above to convert $c_i^+$ to $c_i^+$, as we did above. As above, we have

\begin{align*}
e^{-\nu(\lambda)X_i} c_i^+ &= e^{-\nu(\lambda)X_i} c_i^- + \mathcal{O}\Big( e^{-\tilde{\alpha} X_m} |\tilde{c}| + e^{-\tilde{\alpha} X_m}(|\lambda| + |D| ) |d| \Big) \\
\end{align*}

which gives us

\begin{align*}
\langle \Psi(0), P_i^+(0; \lambda)e^{-\nu(\lambda) X_i} P^c(\lambda) c_i^+ \rangle 
&= \mathcal{O}(|\lambda|) \tilde{c}_i^- + \mathcal{O}\Big( |\lambda|( e^{-\tilde{\alpha} X_m} |\tilde{c}| + e^{-\tilde{\alpha} X_m}(|\lambda| + |D| ) |d| ) \Big)
\end{align*}

\item For the center integral term, we have

\begin{align*}
&\langle \Psi(0), P_i^-(0; \lambda)
\int_{-X_{i-1}}^0 \Phi^c(0, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy \rangle \\
&= \int_{-X_{i-1}}^0 \langle \Psi(0), P_i^-(0; \lambda) \Phi^c(0, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) \rangle dy \\
&= \int_{-X_{i-1}}^0 \langle \Psi(0), \Theta^c(0, y; \lambda) \tilde{H}_i^-(y) \rangle dy \\
&= \int_{-X_{i-1}}^0 \langle \Psi(0), \Theta^c(0, y; 0) \tilde{H}_i^-(y) \rangle dy + \mathcal{O}(|\lambda|) \\
&= \mathcal{O}(|\lambda|)
\end{align*}

\end{enumerate}

Putting this all together, we have

\begin{align*}
\xi_i = \langle \Psi(X_i), P_0^u(0) D_i d \rangle
+ \langle \Psi(-X_{i-1}), P_0^s(0) D_{i-1} d \rangle 
+ \lambda_2 d_i M + R(\lambda)(\tilde{c}, d)
\end{align*}

where $M$ is the higher order Melnikov integral

\[
\int_{-\infty}^\infty \langle \Psi(y), H(y) \rangle dy 
\]

and the remainder term has bound

\begin{align*}
|R(\lambda)(\tilde{c}, d)| \leq C \Big(
|\lambda||\tilde{c}| + |\lambda|(|\lambda|^2 + e^{-\alpha X_m}|\lambda| + e^{-(\alpha + \tilde{\alpha}) X_m})|d| + (e^{-\alpha X_m} |\lambda| + e^{-(\alpha + \tilde{\alpha}) X_m})|D||d|
 \Big)
\end{align*}

Using the fact that $|D| = \mathcal{O}(e^{-\alpha X_m})$, this becomes

\begin{align*}
|R(\lambda)(\tilde{c}, d)| \leq C \Big(
|\lambda||\tilde{c}| + (|\lambda|^3 + e^{-\alpha X_m}|\lambda|^2 + e^{-(\alpha + \tilde{\alpha}) X_m}|\lambda| + e^{-(2 \alpha + \tilde{\alpha}) X_m})|d|
 \Big)
\end{align*}

\subsubsection*{Jump in Y0 direction}

For this jump, we project on $Y_0$.

\[
\xi^c_i = P(Y^0) ( P_i^+(0; \lambda) Z_i^+(0) - P_i^-(0; \lambda) Z_i^-(0) )
\]

We can choose to either project $W_i^\pm(0) = P_i^\pm(0; \lambda) Z_i^\pm(0)$ on $Y_0$ or $Z_i^\pm(0)$ on $E^c(0)$. We can make this choice for each element in the sum, so we will do whatever is easiest.\\

Recall that $Z_i^\pm(0)$ are given by

\begin{align*}
Z_i^-(0) &= \Phi^s(0, -X_{i-1}; \lambda) a_{i-1}^- + b_i^- + (\Phi^u(0, 0; \lambda) - I)b_i^- 
+ e^{\nu(\lambda) X_{i-1}} [P^c(0) c_{i-1}^- + (P^c(\lambda) - P^c(0))c_{i-1}^-] \\
&+ \lambda^2 d_i \int_{-X_{i-1}}^0 \Phi^s(0, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy 
+ \lambda^2 d_i \int_{-X_{i-1}}^0 \Phi^c(0, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy  \\ 
Z_i^+(0) &= \Phi^u(0, X_i; \lambda) a_i^+ + b_i^+ + (\Phi^s(0, 0; \lambda) - I) b_i^+ + e^{-\nu(\lambda)X_i} [P^c(0) c_i^+ + (P^c(\lambda) - P^c(0))c_i^+] \\
&+ \lambda^2 d_i \int_{X_i}^0 \Phi^u(0, y; \lambda) P_i^+(y; \lambda)^{-1} \tilde{H}_i^+(y) dy 
+ \lambda^2 d_i \int_{X_i}^0 \Phi^c(0, y; \lambda) P_i^+(y; \lambda)^{-1} \tilde{H}_i^+(y) dy \\
\end{align*}

The lower order terms will be $e^{\nu(\lambda) X_{i-1}} c_{i-1}^- = \tilde{c}_{i-1}^+$ and $e^{-\nu(\lambda) X_{i-1}} c_-^- = \tilde{c}_{i}^i$ together with the center integral. For the center integral term, we have

\begin{align*}
&\langle Y_0, P_i^-(0; \lambda) \int_{-X_{i-1}}^0 \Phi^c(0, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy \rangle \\
&= \langle \Psi^c(0), \int_{-X_{i-1}}^0 P_i^-(0; \lambda) \Phi^c(0, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy \rangle \\
&= \int_{-X_{i-1}}^0 \langle \Psi^c(0), \Theta^c(0, y; \lambda) \tilde{H}_i^-(y) \rangle dy \\
&= \int_{-X_{i-1}}^0 \langle \Psi^c(0), \Theta^c(0, y; 0) \tilde{H}_i^-(y) \rangle dy + \mathcal{O}(|\lambda|)\\
&= \int_{-X_{i-1}}^0 \langle \Psi^c(y), \tilde{H}_i^-(y) \rangle dy + \mathcal{O}(|\lambda|)\\
&= \int_{-\infty}^0 \langle \Psi^c(y), H(y) \rangle dy + \mathcal{O}(|\lambda| + e^{-\tilde{\alpha}X_{i-1}})
\end{align*}

The other integral is similar. The remainder of the terms are either eliminated or higher order. Since $b_i^\pm \in E^{s/u}$, they are eliminated.
Going through those one at a time (only doing the negative piece, since the other is similar), we have

\begin{enumerate}
\item For the term involving $a$,
\begin{align*}
P_0^c(0) \Phi^s(0, -X_{i-1}; \lambda) a_{i-1}^- &= 
(P_0^c(0) - P_0^c(\lambda)) \Phi^s(0, -X_{i-1}; \lambda) a_{i-1}^- + P_0^c(\lambda) \Phi^s(0, -X_{i-1}; \lambda) a_{i-1}^- \\
&= (P_0^c(0) - P_0^c(\lambda)) \Phi^s(0, -X_{i-1}; \lambda) a_{i-1}^-
\end{align*}

Thus we have
\begin{align*}
|P_0^c(0) \Phi^s(0, -X_{i-1}; \lambda) a_{i-1}^-| 
&\leq C |\lambda| e^{-\alpha X_{i-1}}| P_0^s(\lambda) D_{i-1} d + A_4(\lambda)_{i-1}^-(b, d)| \\
&\leq C |\lambda| e^{-\alpha X_{i-1}}| \Big( e^{-\tilde{\alpha} X_m} |\tilde{c}| + e^{-(\alpha - \rho) X_i} |\lambda|^2|d| + |D||d| \Big)
\end{align*}

\item For the involving $b$ which is not eliminated,
\begin{align*}
|P_0^c(0)  (\Phi^u(0, 0; \lambda) - I)b_i^-| &\leq C |\lambda| |B_1(\lambda)(\tilde{c}, d)| \\
&\leq  C |\lambda| \Big( (|\lambda| + e^{-\tilde{\alpha}X_m})|\tilde{c}|
+ (e^{-\tilde{\alpha}X_m}|D| 
+ |\lambda|^2)|d| \Big)
\end{align*}

\item For the higher order terms involving $c$, we have

\[
P_0^c(0) e^{\nu(\lambda) X_{i-1}} (P^c(\lambda) - P^c(0))c_{i-1}^- 
= \mathcal{O}(|\lambda||\tilde{c}_{i-1}^+|)
\]

We also have to convert $c_i^+$ to $c_i^+$, as we did above. Plugging in for $B_1$, this becomes

\begin{align*}
e^{-\nu(\lambda)X_i} c_i^+ &= e^{-\nu(\lambda)X_i} c_i^- + \mathcal{O}\Big( e^{-\tilde{\alpha} X_m} |\tilde{c}| + e^{-\tilde{\alpha} X_m}(|\lambda| + |D| ) |d| \Big) \\
\end{align*}

\item For the noncenter integral terms,

\begin{align*}
&P_0^c(0) \lambda^2 d_i \int_{-X_{i-1}}^0 \Phi^s(0, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy \\
&= [(P_0^c(0) - P_0^c(\lambda)) + P_0^c(\lambda)] \lambda^2 d_i \int_{-X_{i-1}}^0 \Phi^s(0, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy \\
&= (P_0^c(0) - P_0^c(\lambda)) \lambda^2 d_i \int_{-X_{i-1}}^0 \Phi^s(0, y; \lambda) P_i^-(y; \lambda)^{-1} \tilde{H}_i^-(y) dy \\
&= \mathcal{O}(|\lambda|^3 |d| )
\end{align*}

\end{enumerate}

Putting all of this together, we have

\begin{align*}
\xi^c_i = \tilde{c}_i^- - \tilde{c}_{i-1}^+ - \lambda_2 d_i M^c + R^c(\lambda)(\tilde{c}, d)
\end{align*}

where $M^c$ is the center Melnikov integral

\[
\int_{-\infty}^\infty \langle \Psi^c(y), H(y) \rangle dy 
\]

and the remainder term $R^c(\tilde{c}, d)$ has bound

\begin{align*}
|R^c(\lambda)(\tilde{c}, d)| 
\leq C \Big( (e^{-\tilde{\alpha}X_m} + |\lambda|)|\tilde{c}| + e^{-\tilde{\alpha}X_m}(|\lambda| + |D|)|d| \Big)
\end{align*}

Since $|D| = \mathcal{O}(e^{-\alpha X_m})$, this becomes

\begin{align*}
|R^c(\lambda)(\tilde{c}, d)| 
\leq C \Big( (|\lambda| + e^{-\tilde{\alpha}X_m})|\tilde{c}| + e^{-\tilde{\alpha}X_m}(|\lambda| + e^{-\alpha X_m})|d| \Big)
\end{align*}


\end{document}